TINET+TECS: Component-Based TCP/IP Protocol Stack for Embedded Systems

### 2017-04-16 ICESS2017/paper.tex
Fix figures in evaluation
Final version

The Internet of Things (IoT) is an essential next evolutionary step for the Internet \cite{par:IoTIndustries} \cite{par:IoTComputing} in which various items and platforms, for example, wearable devices and smart devices, will be connected via the Internet to further enrich people's lives.
However, as the IoT uses embedded systems such as data sensors and controlling actuators as elemental constituents, it is often not practical to implement the same Transmission Control Protocol/Internet Protocol (TCP/IP) protocol stacks used by traditional computing systems because embedded systems face restrictions in terms of low memory capacity.

Tomakomai InterNETworking (TINET) is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
As TINET supports functionalities such as a minimum copy frequency and the elimination of dynamic memory control, it requires significantly reduced memory for its TCP/IP protocol stack and is therefore suitable for embedded systems.
However, TINET comprises many complex source codes, i.e., it contains many files and defines many macros, which can be problematic for software developers seeking to maintain, extend, and analyze the software.
Thus, embedded network software is required for high productivity and quality.

One approach to improving software productivity is component-based development, a design technique that can be applied in reusable software development for embedded systems \cite{par:Crnkovic}\cite{par:CBD} such as TECS \cite{par:TECS} \cite{par:hr-tecs}, AUTOSAR \cite{url:AUTOSAR}, or SaveCCM \cite{par:SAVEapproach}.
Component-based systems are flexible to software extension and specification changes.

@@

In TINET, the amount of data copying between each protocol layers is minimized.
In standard computing systems, the TCP/IP protocol stack has large overheads in terms of execution time and memory consumption because the data are copied at each protocol layer.
To solve this problem, TINET does passes the pointer of the data buffer between each protocol layer instead of performing data copying.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/TINETHierarchyDiagram.pdf}
    \vspace{-1mm} \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
    \vspace{-1mm} \label{fig:TINETHierarchyDiagram}
\end{figure}

@@

In TECS, component deployment and composition are performed statically, and as a consequently, component connection does not incur significant overhead, and memory requirements can be reduced.
TECS has various features such as source level portability and fine-grained components and can be implemented in C.

@@

Fig. \ref{fig:ComponentDiagram} shows a component diagram.
{\it Cells}, which are instance of components in TECS, consist of {\it entry} ports, {\it call} ports, attributes, and internal variables.
An {\it entry} port is an interface that provides functions to other {\it cells}, whereas a {\it call} port is an interface that enables the use of other {\it cells}' functions.
Each {\it cell} has one or more {\it entry} ports and {\it call} ports.
{\it Cell} functions are implemented in C.

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sIPv4Output {
  T_IN4_ADDR getIPv4Address(void);
  ER         getOffset([inout]T_OFF_BUF *offset);
  ER         setHeader([inout,size_is(size)]
                        int8_t *outputp,
                        [in]int32_t size,
                        [in]T_IN4_ADDR dstaddr,
                        [in]T_IN4_ADDR srcaddr);
    /* Omit: other functions */
};
\end{lstlisting}
\vspace{-1mm} \caption{Signature description}
\vspace{-1mm} \label{src:signature}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tIPv4Output {
    /* Entry port */
    entry sIPv4Output eOutput;
    /* Call port */
    call sEthernetOutput cEthernetOutput;
    /* Omit: other call ports */
    attr {  /* Attribute */
        uint16_t fragInit = 0;
    };
    var {   /* Variable */
        uint16_t fragId = fragInit;
    };
};
\end{lstlisting}
\vspace{-1mm} \caption{Celltype description}
\vspace{-1mm} \label{src:celltype}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tIPv4Output IPv4Output {
    /* Omit: other build description */
    fragInit = 0; /* Attribute */
};
cell tTCPOutput TCPOutput {
    cIPv4Output = IPv4Output.eOutput;
    /* Omit: other build description */
};
\end{lstlisting}
\vspace{-1mm} \caption{Build description}
\vspace{-1mm} \label{src:build}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/tMemoryAllocator.pdf}
    \vspace{-1mm} \caption{Component diagram of tMemoryAllocator}
    \vspace{-1mm} \label{fig:tMemoryAllocator}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/SendReceive.pdf}
    \vspace{-1mm} \caption{Differences between in/out and send/receive}
    \vspace{-1mm} \label{fig:SendReceive}
\end{figure}

@@

As shown in Fig. \ref{src:SendReceive}, data sending and receiving arguments such as {\it outputp} and {\it inputp} are defined using, respectively, the {\it send/receive} specifier in the signature description.

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sNicDriver {
  void start(
    [send(sNetworkAlloc),size_is(size)]
        int8_t *outputp,
    [in]int32_t size,
    [in]uint8_t align);
  void read(
    [receive(sNetworkAlloc),size_is(*size)]
        int8_t **inputp,
    [out]int32_t *size,
    [in]uint8_t align);
    /* Omit: other functions */
};
\end{lstlisting}
\vspace{-1mm} \caption{Signature description of the nic driver (An example of send/receive)}
\vspace{-1mm} \label{src:SendReceive}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/DynamicConnection.pdf}
    \vspace{-1mm} \caption{Dynamic connection}
    \vspace{-1mm} \label{fig:DynamicConnection}
\end{figure}

TECS supports dynamic connection, a method for switching the binding of components at runtime (Fig. \ref{fig:DynamicConnection}) as a new functionality.
In Fig. \ref{fig:DynamicConnection}, the solid line represents binding and the dotted line represents non-binding.
Note that all components are statically generated in TECS, which can optimize the overhead of componentization because components are statically configured.
Dynamically generating components causes a good deal of memory consumption, which is a serious problem for embedded systems with strict memory constraints.
The proposed framework can take advantage of the componentization in TINET while satisfying the memory constraint because components are statically generated and dynamically connected in TECS.

TINET+TECS utilizes dynamic connection to switch between CEP and REP components, as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
In a server application, CEP is associated with REP in the state of waiting for connection request from clients\footnote{tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
For example, when processing with the HTTP protocol, CEP passively opens with an REP of port number 80.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
    \vspace{-1mm} \caption{Dynamic connection between CEP and REP}
    \vspace{-1mm} \label{fig:DynamicConnectionUseCase}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sRepSelector {
    void  getRep([out]Descriptor(sREP4) *desc,
                 [in]int_t i);
};
celltype tRepSelector {
    entry sRepSelector eRepSelector;
    [ref_desc]
        call sREP4 cREP[NUM_REP];
};
celltype tTCPCEP {
    call sRepSelector cRepSelector;
    [dynamic]
        call sREP4 cREP;
    /* Omit: other call/entry ports */
    /* Omit: attributes and variables */
};
\end{lstlisting}
\vspace{-1mm} \caption{Signature and celltype description for dynamic connection}
\vspace{-1mm} \label{src:DynamicCDLcode}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
eAPI_accept (.., ..) {
    /* Get a descriptor of intended REP cell */
    cRepSelector_getRep(&desc, repid);
    /* Set the descriptor */
    cREP_set_descriptor(desc);
    /* Call the function of intended REP cell */
    cREP_getEndpoint();
}
\end{lstlisting}
\vspace{-1mm} \caption{Accept function (Dynamic connection example)}
\vspace{-1mm} \label{src:DynamicCcode}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/TECS_Adapter.pdf}
    \vspace{-1mm} \caption{TECS adapter}
    \vspace{-1mm} \label{fig:TECS_Adapter}
\end{figure}

@@

\subsection{Evaluation environment}

@@

\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Evaluation Board Environment}
    \begin{tabular}{l|l}
        \hline\hline
        Board           &   GR-PEACH                \\
        CPU             &   Cortex-A9 RZ/A1H 400MHz \\
        Flash ROM       &   8 MB                    \\
        RAM             &   10 MB                   \\
        LAN Controller  &   LAN8710A                \\
        \hline
    \end{tabular}
    \label{tab:EvaluationBoardEnvironment}
\end{table}

@@

The {\it tcp\_snd\_dat} and {\it tcp\_rcv\_dat} APIs were used in the evaluation to, respectively, send and receive TCP data.
For {\it tcp\_snd\_dat}, we measured the executing time starting from the API call through the application until the return of the processing result.
In TINET+TECS, this process is performed in the order tApplication, tTCPCEP, tTCPOutputTaskBody, tIPv4Output, tEthernetOutput, tArp, tEthernetOutputTaskBody, and tIfMbed, as shown in Fig. \ref{fig:ComponentProtocolStack}.
For {\it tcp\_rcv\_dat}, we measured the execution time from the data receipt in the LAN driver until data acquisition in the application.
In TINET+TECS, the process is performed in the order tIfMbed, tEthernetInputTaskBody, tIPv4Input, tTCPInput, tTCPCEP, and tApplication, as shown in Fig. \ref{fig:ComponentProtocolStack}.
The execution time of TINET+TECS is close to that of TINET, with an overhead of about 3 ms.
As the use of the {\it send/receive} specifier enables accessing of the buffer address without data copying, the componentization overhead does not affect the execution time.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/EvaluationOfExecutionTime.pdf}
    \vspace{-1mm} \caption{Execution times of TINET and TINET+TECS}
    \vspace{-1mm} \label{fig:EvaluationOfExecutionTime}
\end{figure}

@@

\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Memory consumption of TINET and TINET+TECS}
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                    &   text       &  data    &   bss      &  total     \\ \hline
        TINET       &   183.94 KB  &  5.37 KB &  132.03 KB &  322.34 KB \\
        TINET+TECS  &   170.73 KB  &  5.37 KB &  149.13 KB &  325.23 KB \\
        \hline
        \multicolumn{5}{r}{Including the application and kernel objects}
    \end{tabular}
    \label{tab:EvaluationOfMemoryConsumption}
\end{table}

@@

\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Modified code lines of CDL}
    \begin{tabular}{c|r|r|r}
        \hline\hline
                         &   Size       &   Size (-- Default) & CDL  \\ \hline
        Default          &   325.23 KB  &              0 KB   &  0 lines   \\
        I                &   305.40 KB  &       -- 19.83 KB   & 18 lines   \\
        I + I\hspace{-.1em}I &   304.12 KB  &   -- 21.10 KB   & 27 lines   \\
        I + I\hspace{-.1em}I + I\hspace{-.1em}I\hspace{-.1em}I & 303.45 KB & -- 21.77 KB  & 32 lines \\
        \hline
        \multicolumn{4}{l}{I: Remove TCP}\\
        \multicolumn{4}{l}{I\hspace{-.1em}I: Remove ICMP}\\
        \multicolumn{4}{l}{I\hspace{-.1em}I\hspace{-.1em}I: Change network buffer (Remove memory pools)}
    \end{tabular}
    \label{tab:EvaluationOfConfigurability}
\end{table}

@@

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
%     \vspace{-1mm} \caption{Memory consumption in two cases (with/without dynamic connection)}
%     \vspace{-1mm} \label{fig:EvaluationOfDynamicConnection}
% \end{figure}
\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Memory consumption in two cases\protect\linebreak (with/without dynamic connection)}
    {\tabcolsep = 1mm
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                &  CEP:1 REP:1 & CEP:1 REP:5 & CEP:2 REP:5 & CEP:5 REP:10 \\ \hline
        without &  324.98 KB   & 325.34 KB   & 326.39 KB   & 331.68 KB   \\
        with    &  325.23 KB   & 325.32 KB   & 327.24 KB   & 330.48 KB   \\
        \hline
    \end{tabular}
    }
    \label{fig:EvaluationOfDynamicConnection}
\end{table}

\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{CDL code lines of without/with dynamic connection}
    \begin{tabular}{l|r|r|r}
        \hline\hline
                     &  without  &  with  &  Diff  \\ \hline
        CEP:1 REP:1  &  344 lines     &  347 lines  &  -3 lines   \\
        CEP:1 REP:5  &  369 lines     &  367 lines  &   2 lines   \\
        CEP:2 REP:5  &  387 lines     &  382 lines  &   5 lines   \\
        CEP:5 REP:10 &  485 lines     &  445 lines  &  40 lines   \\
        \hline
    \end{tabular}
    \label{tab:EvaluationOfConfigurabilityByDynamicConnection}
\end{table}

\begin{figure}[t]
 \centering
 \begin{lstlisting}
/* without Dynamic Connection */
cell tTCPCEP TCPCEP_000 {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_001 {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
..
cell tTCPCEP TCPCEP_00n {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
 \end{lstlisting}
 \centering
 \begin{lstlisting}
/* with Dynamic Connection */
cell tRepSelector RepSelector {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_000 {
    cRepSelector = RepSelector.eRepSelector;
};
cell tTCPCEP TCPCEP_001 {
    cRepSelector = RepSelector.eRepSelector;
};
..
cell tTCPCEP TCPCEP_00n {
    cRepSelector = RepSelector.eRepSelector;
};
 \end{lstlisting}
 \vspace{-1mm} \caption{Two CDL codes (without/with dynamic connection)}
 \vspace{-1mm} \label{src:ComparisonOfCDL}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/EvaluationOfAdapter.pdf}
    \vspace{-1mm} \caption{Execution times in two cases (without/with TECS adapter)}
    \vspace{-1mm} \label{fig:EvaluationOfAdapter}
\end{figure}

@@

@@

Open-source TCP/IP protocol stacks for embedded systems have been developed such uIP \cite{par:uIP} and lwIP \cite{par:lwIP}.

@@

{\bf lwIP:}
lwIP (lightweightIP) is a small TCP/IP implementation for embedded systems that is intended to reduce memory resource usage while still maintaining a full-scale TCP.
lwIP requires about 40 KB of ROM and tens of KB of RAM.
lwIP is larger than uIP, but provides better throughput.

@@

In future work, we will adapt the proposed framework to cooperate with mruby on TECS \cite{par:mrubyonTECS} to more easily manage IoT devices.
Note that mruby is a scripting language for embedded systems \cite{par:mruby}.
We will support functionalities in which TINET functions can be utilized from mruby programs as an extension of mruby-socket \cite{url:mruby-library}.

>>>>

The Internet of Things (IoT) is an essential next evolutionary step for the Internet \cite{par:IoTComputing} in which various items and platforms, for example, wearable devices and smart devices, will be connected via the Internet to further enrich people's lives.
However, as the IoT uses embedded systems such as data sensors and controlling actuators as elemental constituents, it is often not practical to implement the same Transmission Control Protocol/Internet Protocol (TCP/IP) protocol stacks used by traditional computing systems because embedded systems face restrictions in terms of low memory capacity.

Tomakomai InterNETworking (TINET) is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
As TINET supports functionalities such as a minimum copy frequency and the elimination of dynamic memory control, it requires significantly reduced memory for its TCP/IP protocol stack and is, therefore, suitable for embedded systems.
However, TINET comprises many complex source codes, i.e., it contains many files and defines many macros, which can be problematic for software developers seeking to maintain, extend, and analyze the software.
Thus, embedded network software is required for high productivity and quality.

One approach to improving software productivity is component-based development (CBD), a design technique that can be applied in reusable software development for embedded systems \cite{par:Crnkovic}\cite{par:CBD} such as TECS \cite{par:TECS} \cite{par:hr-tecs}, AUTOSAR \cite{url:AUTOSAR}, or SaveCCM \cite{par:SAVEapproach}.
Component-based systems are flexible to software extension and specification changes.

@@

In TINET, the amount of data copying between each protocol layers is minimized.
In standard computing systems, the TCP/IP protocol stack has large overheads in terms of execution time and memory consumption because the data are copied at each protocol layer.
To solve this problem, TINET does pass the pointer of the data buffer between each protocol layer instead of performing data copying.

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/TINETHierarchyDiagram.pdf}
    \vspace{-1mm} \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
    \vspace{-1mm} \label{fig:TINETHierarchyDiagram}
\end{figure}

@@

In TECS, component deployment and composition are performed statically, and as a consequently, a component connection does not incur significant overhead, and memory requirements can be reduced.
TECS has various features such as source level portability and fine-grained components and can be implemented in C.

@@

Fig. \ref{fig:ComponentDiagram} shows a component diagram.
{\it Cells}, which are instances of components in TECS, consist of {\it entry} ports, {\it call} ports, attributes, and internal variables.
An {\it entry} port is an interface that provides functions to other {\it cells}, whereas a {\it call} port is an interface that enables the use of other {\it cells}' functions.
Each {\it cell} has one or more {\it entry} ports and {\it call} ports.
{\it Cell} functions are implemented in C.

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sIPv4Output {
  T_IN4_ADDR getIPv4Address(void);
  ER         getOffset([inout]T_OFF_BUF *offset);
  ER         setHeader([inout,size_is(size)]
                        int8_t *outputp,
                        [in]int32_t size,
                        [in]T_IN4_ADDR dstaddr,
                        [in]T_IN4_ADDR srcaddr);
    /* Omit: other functions */
};
\end{lstlisting}
\vspace{-2mm} \caption{Signature description}
\vspace{-1mm} \label{src:signature}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tIPv4Output {
    /* Entry port */
    entry sIPv4Output eOutput;
    /* Call port */
    call sEthernetOutput cEthernetOutput;
    attr {  /* Attribute */
        uint16_t fragInit = 0;
    };
    var {   /* Variable */
        uint16_t fragId = fragInit;
    };
};
\end{lstlisting}
\vspace{-2mm} \caption{Celltype description}
\vspace{-1mm} \label{src:celltype}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tIPv4Output IPv4Output {
    fragInit = 0; /* Attribute */
};
cell tTCPOutput TCPOutput {
    cIPv4Output = IPv4Output.eOutput;
};
\end{lstlisting}
\vspace{-2mm} \caption{Build description}
\vspace{-1mm} \label{src:build}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/tMemoryAllocator.pdf}
    \vspace{-1mm} \caption{Component diagram of tMemoryAllocator}
    \vspace{-1mm} \label{fig:tMemoryAllocator}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/SendReceive.pdf}
    \vspace{-1mm} \caption{Differences between in/out and send/receive}
    \vspace{-1mm} \label{fig:SendReceive}
\end{figure}

@@

As shown in Fig. \ref{src:SendReceive}, sending and receiving arguments such as {\it outputp} and {\it inputp} are defined using, respectively, the {\it send/receive} specifier in the signature description.
Developers hardly make mistakes of memory operation because these specifiers completely pass an ownership of memory.
Common object request broker architecture (CORBA) does not consider memory sharing; CORBA has no functionalities
such as {\it send}/{\it receive}.

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sNicDriver {
  void start(
    [send(sNetworkAlloc),size_is(size)]
        int8_t *outputp, .., ..);
  void read(
    [receive(sNetworkAlloc),size_is(*size)]
        int8_t **inputp, .., ..);
    /* Omit: other functions */
};
\end{lstlisting}
\vspace{-2mm} \caption{Signature description of the nic driver (An example of send/receive)}
\vspace{-1mm} \label{src:SendReceive}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/DynamicConnection.pdf}
    \vspace{-3mm} \caption{Dynamic connection}
    \vspace{-1mm} \label{fig:DynamicConnection}
\end{figure}

TECS supports a dynamic connection, a method for switching the binding of components at runtime (Fig. \ref{fig:DynamicConnection}) as a new functionality.
In Fig. \ref{fig:DynamicConnection}, the solid line represents binding and the dotted line represents non-binding.
Note that all components are statically generated in TECS, which can optimize the overhead of componentization because components are statically configured.
Dynamically generating components causes a good deal of memory consumption, which is a serious problem for embedded systems with strict memory constraints.
The proposed framework can take advantage of the componentization in TINET while satisfying the memory constraint because components are statically generated and dynamically connected in TECS.

TINET+TECS utilizes the dynamic connection to switch between CEP and REP components, as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
In a server application, CEP is associated with REP in the state of waiting for connection request from clients\footnote{tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
For example, when processing with the HTTP protocol, CEP passively opens with an REP of port number 80.

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
    \vspace{-1mm} \caption{Dynamic connection between CEP and REP}
    \vspace{-1mm} \label{fig:DynamicConnectionUseCase}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sRepSelector {
    void  getRep([out]Descriptor(sREP4) *desc,
                 [in]int_t i);
};
celltype tRepSelector {
    entry sRepSelector eRepSelector;
    [ref_desc]
        call sREP4 cREP[NUM_REP];
};
celltype tTCPCEP {
    call sRepSelector cRepSelector;
    [dynamic]
        call sREP4 cREP;
    /* Omit: other call/entry ports */
    /* Omit: attributes and variables */
};
\end{lstlisting}
\vspace{-2mm} \caption{Signature and celltype description for dynamic connection}
\vspace{-1mm} \label{src:DynamicCDLcode}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
eAPI_accept (.., ..) {
    /* Get a descriptor of intended REP cell */
    cRepSelector_getRep(&desc, repid);
    /* Set the descriptor */
    cREP_set_descriptor(desc);
    /* Call the function of intended REP cell */
    cREP_getEndpoint();
}
\end{lstlisting}
\vspace{-2mm} \caption{Accept function (Dynamic connection example)}
\vspace{-1mm} \label{src:DynamicCcode}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/TECS_Adapter.pdf}
    \vspace{-1mm} \caption{TECS adapter}
    \vspace{-1mm} \label{fig:TECS_Adapter}
\end{figure}

@@

% \subsection{Evaluation environment}

@@

\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Evaluation Board Environment}
\vspace{-2mm}
    \begin{tabular}{l|l}
        \hline\hline
        Board           &   GR-PEACH                \\
        CPU             &   Cortex-A9 RZ/A1H 400MHz \\
        Flash ROM       &   8 MB                    \\
        RAM             &   10 MB                   \\
        LAN Controller  &   LAN8710A                \\
        \hline
    \end{tabular}
    \label{tab:EvaluationBoardEnvironment}
\end{table}

@@

The {\it tcp\_snd\_dat} and {\it tcp\_rcv\_dat} APIs were used in the evaluation to, respectively, send and receive TCP data.
For {\it tcp\_snd\_dat}, we measured the executing time starting from the API call through the application until the return of the processing result.
In TINET+TECS, this process is performed in the order tApplication, tTCPCEP, tTCPOutputTaskBody, tIPv4Output, tEthernetOutput, tArp, tEthernetOutputTaskBody, and tIfMbed, as shown in Fig. \ref{fig:ComponentProtocolStack}.
For {\it tcp\_rcv\_dat}, we measured the execution time from the data receipt in the LAN driver until data acquisition in the application.
In TINET+TECS, the process is performed in the order tIfMbed, tEthernetInputTaskBody, tIPv4Input, tTCPInput, tTCPCEP, and tApplication, as shown in Fig. \ref{fig:ComponentProtocolStack}.
The execution time of TINET+TECS is close to that of TINET, with an overhead of about 3 us.
As the use of the {\it send/receive} specifier enables accessing of the buffer address without data copying, the componentization overhead does not affect the execution time.

\begin{figure}[t]
    \centering
    \includegraphics[width=7.5cm,clip]{figure/EvaluationOfExecutionTime.pdf}
    \vspace{-1mm} \caption{Execution times of TINET and TINET+TECS}
    \vspace{-1mm} \label{fig:EvaluationOfExecutionTime}
\end{figure}

@@

\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Memory consumption of TINET and TINET+TECS}
\vspace{-2mm}
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                    &   text       &  data    &   bss      &  total     \\ \hline
        TINET       &   183.94 KB  &  5.37 KB &  132.03 KB &  322.34 KB \\
        TINET+TECS  &   170.73 KB  &  5.37 KB &  149.13 KB &  325.23 KB \\
        \hline
        \multicolumn{5}{r}{Including the application and kernel objects}
    \end{tabular}
    \label{tab:EvaluationOfMemoryConsumption}
\end{table}

@@

\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Modified code lines of CDL}
\vspace{-2mm}
    \begin{tabular}{c|r|r|r}
        \hline\hline
                         &   Size       &   Size (-- Default) & CDL  \\ \hline
        Default          &   325.23 KB  &              0 KB   &  0 lines   \\
        I                &   305.40 KB  &       -- 19.83 KB   & 18 lines   \\
        I + I\hspace{-.1em}I &   304.12 KB  &   -- 21.10 KB   & 27 lines   \\
        I + I\hspace{-.1em}I + I\hspace{-.1em}I\hspace{-.1em}I & 303.45 KB & -- 21.77 KB  & 32 lines \\
        \hline
        \multicolumn{4}{l}{I: Remove TCP}\\
        \multicolumn{4}{l}{I\hspace{-.1em}I: Remove ICMP}\\
        \multicolumn{4}{l}{I\hspace{-.1em}I\hspace{-.1em}I: Change network buffer (Remove memory pools)}
    \end{tabular}
\vspace{-3mm}
    \label{tab:EvaluationOfConfigurability}
\end{table}

@@

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
%     \vspace{-1mm} \caption{Memory consumption in two cases (with/without dynamic connection)}
%     \vspace{-1mm} \label{fig:EvaluationOfDynamicConnection}
% \end{figure}
\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Memory consumption in two cases\protect\linebreak (with/without dynamic connection)}
\vspace{-2mm}
    {\tabcolsep = 1mm
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                &  CEP:1 REP:1 & CEP:1 REP:5 & CEP:2 REP:5 & CEP:5 REP:10 \\ \hline
        without &  324.98 KB   & 325.34 KB   & 326.39 KB   & 331.68 KB   \\
        with    &  325.23 KB   & 325.32 KB   & 327.24 KB   & 330.48 KB   \\
        \hline
    \end{tabular}
    }
    \label{fig:EvaluationOfDynamicConnection}
\end{table}

\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{CDL code lines of without/with dynamic connection}
\vspace{-2mm}
    \begin{tabular}{l|r|r|r}
        \hline\hline
                     &  without  &  with  &  Diff  \\ \hline
        CEP:1 REP:1  &  344 lines     &  347 lines  &  -3 lines   \\
        CEP:1 REP:5  &  369 lines     &  367 lines  &   2 lines   \\
        CEP:2 REP:5  &  387 lines     &  382 lines  &   5 lines   \\
        CEP:5 REP:10 &  485 lines     &  445 lines  &  40 lines   \\
        \hline
    \end{tabular}
    \label{tab:EvaluationOfConfigurabilityByDynamicConnection}
\end{table}

\begin{figure}[t]
 \centering
 \begin{lstlisting}
/* without Dynamic Connection */
cell tTCPCEP TCPCEP_000 {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_001 {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
..
cell tTCPCEP TCPCEP_00n {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
 \end{lstlisting}
 \vspace{-2mm}
 \centering
 \begin{lstlisting}
/* with Dynamic Connection */
cell tRepSelector RepSelector {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_000 {
    cRepSelector = RepSelector.eRepSelector;
};
cell tTCPCEP TCPCEP_001 {
    cRepSelector = RepSelector.eRepSelector;
};
..
cell tTCPCEP TCPCEP_00n {
    cRepSelector = RepSelector.eRepSelector;
};
 \end{lstlisting}
 \vspace{-2mm} \caption{Two CDL codes (without/with dynamic connection)}
 \vspace{-1mm} \label{src:ComparisonOfCDL}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=7.5cm,clip]{figure/EvaluationOfAdapter.pdf}
    \vspace{-1mm} \caption{Execution times in two cases (without/with TECS adapter)}
    \vspace{-1mm} \label{fig:EvaluationOfAdapter}
\end{figure}

@@

\begin{table*}[t]
    \caption{Comparison of related and proposed framework}
    \label{tab:comparison}
\vspace{-2mm}
    \centering
    \begin{tabular}{c||ccccccc}
        \hline\hline
        & \shortstack{Configurability}
        & \shortstack{Generation} 
        & \shortstack{Binding} 
        & \shortstack{Support CBD} 
        & \shortstack{Memory saving} \\ \hline
        uIP \cite{par:uIP}     & $\bigtriangleup$          & Dynamic    & Dynamic  &              & \checkmark \\
        lwIP \cite{par:lwIP}   & $\bigtriangleup$          & Dynamic    & Dynamic  &              & \checkmark \\
        TINET \cite{url:TINET} &            & Static     & Dynamic  &              & \checkmark \\
        Proposed framework     & \checkmark & Static     & Dynamic  & \checkmark   & \checkmark \\
    \end{tabular}
        \vspace{-5mm}
\end{table*}

@@

Table \ref{tab:comparison} shows a comparison of TINET+TECS and previous work.
Open-source TCP/IP protocol stacks for embedded systems have been developed such uIP \cite{par:uIP} and lwIP \cite{par:lwIP}.

@@

{\bf lwIP:}
lwIP (lightweightIP) is a small TCP/IP implementation for embedded systems that is intended to reduce memory resource usage while still maintaining a full-scale TCP.
lwIP requires about 40 KB of ROM and tens of KB of RAM.
lwIP is larger than uIP, but provides better throughput.
To customize protocols and buffer size, users should handle a lot of macros.

Note that the proposed framework, TINET+TECS, has demonstrated all features shown in Table \ref{tab:comparison}.
In particular, TINET+TECS is configurable and is suitable for embedded systems with memory constraint.

@@

In future work, we will adapt the proposed framework to cooperate with mruby on TECS \cite{par:mrubyonTECS}, to more easily manage IoT devices.
We will support functionalities in which TINET functions can be utilized from mruby programs as an extension of mruby-socket \cite{url:mruby-library}.
